SPARQL on the Open, Decentralised Web

### 2016-06-22 dissertation/introdefhistory.tex
Some low-hanging fruit

This chapter serves to tie the accepted papers into a whole, provide
and overarching rationale and problem statements, overview of the
contributions and a discussion of the problematic sides of the study
seen from a philosophy of science viewpoint. It is structured as
follows: Section~\ref{sec:nodef} discusses the possibility of defining
the Semantic Web, Section~\ref{sec:objectivity} discusses the problem
of maintaining objectivity, Section~\ref{sec:history} attempts to
satisfy the previous discussion by detailing the author's personal
involvement in the Semantic Web. Section~\ref{sec:motivation} has an
overview of the motivation behind this work.
Section~\ref{sec:related} puts the present work into the context
within the existing literature. Section~\ref{sec:problems} summarises
important research problems and details the motivation, and
Section~\ref{sec:papersincontext} addresses how the contributions
address these problems and discusses weaknesses of the papers with the
benefit of hindsight. Key insights are finally summarised in
Section~\ref{sec:conclusions}.\todo{Big problem statement here}

@@

The Semantic Web can be described as a machine-readable Web of Data,
defined by a technology stack managed by the World Wide Web
Consortium. While individual technologies can be given precise,
operational definitions, the above definition is naive and can hardly
be used operationally to derive new knowledge. The Semantic Web is a
complex, human artefact that must be understood not only in technical
terms, but also in social, economic and cultural terms. First, the Web
is not only readable, but also writeable. Whether the essential parts
of a data integration problem will be solved by e.g. pervasive
ontology alignment, a linked open vocabularies approach where many
players adopt a fairly consistent set of vocabularies, or by major
players that are able to force convergence towards e.g. \texttt{Schema.org}
is an example of the social, economic and cultural mechanisms that
shape the future of the Semantic Web, see
Section~\ref{sec:semproblems} for a more elaborate
discussion. Likewise, it may not be the W3C Semantic Web stack at all
that achieves success, though unlikely at this point, it may be
something in the extension of microformats\footnote{see
  \url{http://microformats.org/}}, microdata\cite{microdata}, or
something else entirely. For a thoughtful criticism of Linked Data
with a proposed alternative, see \cite{darobin1}, but again, it is
likely that social, economic and cultural factors will be as decisive
as technical. One may say that e.g. microformats cannot help achieve
the visions that may be stated for the Semantic Web, but that again
emphasises visions, not operational definitions.

@@

Therefore, rather than attempt a definition, understanding is rather
promoted by following the example of \cite{berners2001semantic} and
declare a vision.

>>>>

This chapter serves to tie the published papers into a whole, provide
an overarching rationale and problem statements, overview of the
contributions and a discussion of the problematic sides of the study
seen from a philosophy of science viewpoint. It is structured as
follows: Section~\ref{sec:nodef} discusses the possibility of defining
the Semantic Web, Section~\ref{sec:objectivity} discusses the problem
of maintaining objectivity, Section~\ref{sec:history} attempts to
satisfy the previous discussion by detailing the author's personal
involvement in the Semantic Web. Section~\ref{sec:motivation} has an
overview of the motivation behind this work.
Section~\ref{sec:related} puts the present work into the context
within the existing literature. Section~\ref{sec:problems} summarises
important research problems and details the motivation, and
Section~\ref{sec:papersincontext} details how the contributions
address these problems and discusses weaknesses of the papers with the
benefit of hindsight. Key insights are finally summarised in
Section~\ref{sec:conclusions}.\todo{Big problem statement here}

@@

The Semantic Web can be described as a machine-readable Web of Data,
defined by a technology stack managed by the World Wide Web
Consortium. While individual technologies can be given precise,
operational definitions, the above definition is naive and can hardly
be used operationally to derive new knowledge. The Semantic Web is a
complex, human artefact that must be understood not only in technical
terms, but also in social, economic and cultural terms. First, the Web
is not only readable, but also writeable. Whether the essential parts
of a data integration problem will be solved by e.g. pervasive
ontology alignment, a linked open vocabularies approach where many
players adopt a fairly consistent set of vocabularies, or by major
players that are able to force convergence towards e.g. \texttt{Schema.org}
is an example of the social, economic and cultural mechanisms that
shape the future of the Semantic Web, see
Section~\ref{sec:semproblems} for a more elaborate
discussion. Likewise, it may not be the W3C Semantic Web stack at all
that achieves success, though unlikely at this point, it may be
something in the extension of microformats\footnote{See
  \url{http://microformats.org/}}, microdata\cite{microdata}, or
something else entirely. For a thoughtful criticism of Linked Data
with a proposed alternative, see \cite{darobin1}, but again, it is
likely that social, economic and cultural factors will be as decisive
as technical. One may say that e.g. microformats cannot help achieve
the visions that may be stated for the Semantic Web, but that again
emphasises visions, not operational definitions.

@@

Therefore, rather than attempt a definition, understanding is better
promoted by following the example of \cite{berners2001semantic} and
declaring a vision.
